Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-06-29 article-models-ttinternal.tex
initiated the sections on identity terms, substitution (revised) and e-algebras

\subsection{Projection algebras}

\subsection{Substitution algebras}

Let $(A,P,T,\epsilon_0,\epsilon_1,\phi_0,\phi_1)$ be a term-algebra. To define
substitution algebras, we will consider
\begin{align*}
\jhom*
  {{{{\Gamma}{A}}{P}}{T}}
  {\ctxwk{T}{\jcomp{}{\epsilon_0}{P}}}
  {P}
  {\sigma_0}
  \\
\jfhom*
  {{{{\Gamma}{A}}{P}}{T}}
  {\ctxwk{T}{\jcomp{}{\epsilon_0}{P}}}
  {P}
  {\sigma_0}
  {\ctxwk{T}{\jcomp{}{\epsilon_0}{\jcomp{}{\epsilon_0}{P}}}}
  {\jcomp{}{\epsilon_0}{P}}
  {\sigma_1}
  \\
\jfhom*
  {{{{\Gamma}{A}}{P}}{T}}
  { \ctxext
      {\ctxwk{T}{\jcomp{}{\epsilon_0}{P}}}
      {\ctxwk{T}{\jcomp{}{\epsilon_0}{\jcomp{}{\epsilon_0}{P}}}}
    }
  {\ctxext{P}{\jcomp{}{\epsilon_0}{P}}}
  {\jvcomp{}{\sigma_0}{\sigma_1}}
  {\ctxwk{T}{\jcomp{}{\epsilon_0}{\jcomp{}{\epsilon_0}{T}}}}
  {\jcomp{}{\epsilon_0}{T}}
  {\sigma_2}
\end{align*}
for which the pair $(\sigma_0,\sigma_1)$ is required to be an extension
homomorphism and the triple $(\sigma_0,\sigma_1,\sigma_2)$ is required to
be an empty term-homomorphism.

\subsection{E-algebras}

>>>>

\subsection{Projection algebras}
Projection algebras will be weakening algebras with additional terms implementing
the identity terms. We call these algebras projection algebras because the
identity terms can only be formulated in weakening algebras and together with
weakening, the identity terms provide for all the projections. In a weakening
algebra $\cftalg{A}$ in context $\Gamma$, identity terms are implemented by a term
\begin{equation*}
\jterm
  {context}
  {\subst{{\idtm{\cftalgf{\cftalg{A}}}}{\cftwkc{\cftalg{A}}}}{\cftalgt{\cftalg{F_{F_A}}}}}
  {\cftidtm{\cftalg{A}}}
\end{equation*}
We will require additionally that identity terms are compatible with weakening.
Thus we will formulate an abstraction of the rule stated in \autoref{comp-wi}.

\subsection{Substitution algebras}
Substitution algebras will be CFT-algebras with an additional substitution 
operation. Given a CFT-algebra $\cftalg{A}$ in context $\Gamma$, substitution 
will be a CFT-homomorphism
\begin{equation*}
\jhom
  {{{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}{\cftalgt{\cftalg{A}}}}
  {\ctxwk{\cftalgt{\cftalg{A}}}{\cftalg{F_{F_A}}}}
  {\cftalgf{\cftalg{A}}}
  {\cftsubst{\cftalg{A}}}
\end{equation*}
We will require additionally that substitution preserves itself. Thus, we will
formulate an abstraction of the rules stated in \autoref{comp-ss}.

\subsection{E-algebras}
E-algebras will be CFT-algebras with a weakening operation, identity terms and
a substitution operation making it a projection algebra and a substitution 
algebra at the same time. Additionally the weakening operation, identity terms
and the substitution operation are all required to be compatible with each
other. Thus, we need to require the abstractions of the rules stated in
\autoref{comp-sw,comp-ws,cancellation-ws,cancellation-i}.
